Stochastic Convolutional Sparse Coding

### 2018-05-18 nips2018/main.tex
submiited version

% Commenting
\usepackage[colorinlistoftodos,bordercolor=orange,backgroundcolor=orange!20,linecolor=orange,textsize=scriptsize]{todonotes}
\newcommand{\peter}[1]{\todo[inline]{\textbf{Peter: }#1}}

@@

\begin{abstract}
The minimization problems formulated in Convolutional Sparse Coding (CSC) have been solved in frequency domain by modern approaches owing to the improved computing efficiency, while it automatically assumes circular boundary conditions. In this work, we propose a novel stochastic spatial-domain solver where a randomized subsampling strategy is introduced in the subproblem of computing sparse codes. The proposed method experimentally shows a faster convergence rate compared to the state-of-the-art, and with a reasonable selection for the subsampling probability, it also achieves a better runtime efficiency. Moreover, we extend the proposed strategy in conjunction with online learning, scaling the CSC model up to arbitrary sample sizes. This combination leads to a significant speedup over the online CSC algorithm solved in frequency domain. We then learn the over-complete dictionary from thousand of images, which demonstrates a better sparse representation of the natural images on account of more abundant filters.
\end{abstract}

@@

{\small
\bibliographystyle{ieeetr}
\bibliography{egbib}
}

>>>>

@@

\begin{abstract}
The minimization problems formulated in Convolutional Sparse Coding (CSC) have been solved in frequency domain by modern approaches owing to the improved computing efficiency, while it automatically assumes circular boundary conditions. In this work, we propose a novel stochastic spatial-domain solver where a randomized subsampling strategy is introduced in the subproblem of computing sparse codes. The proposed method experimentally shows a faster convergence rate compared to the state-of-the-art, and with a reasonable selection for the subsampling probability, it also achieves a better runtime efficiency. Moreover, we extend the proposed strategy in conjunction with online learning, scaling the CSC model up to arbitrary sample sizes. This combination leads to a significant speedup over the online frequency-domain CSC algorithm. We then learn the over-complete dictionary from large datasets, which demonstrates a better sparse representation of the natural images on account of more abundant filters.
\end{abstract}

@@

%\clearpage
{\small
\bibliographystyle{ieeetr}
\bibliography{egbib}
}

\clearpage
\appendix

\input{supplement.tex}
